### 2021-05-26 Paper.tex
modified

\begin{table}[H]
\caption{List of benchmarks implemented for each feature of the code.}
\centering
\begin{tabular}{| l | l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark} & \textbf{Section} \\
\midrule
  Solver  & Stokes flow & \ref{sec:stokes} \\
\hline
  4th-order Runge-Kutta  & \multirow{2}{*}{Zalesak disk} & \multirow{2}{*}{\ref{sec:runge}} \\
  markers advection  &  & \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow & \ref{sec:poiseuille}\\
    & Instantaneous 2D sphere & \ref{sec:ist_sphere} \\
    & Rayleigh-Taylor experiment & \ref{sec:rayleigh} \\
    & Falling block & \ref{sec:block} \\
\hline
    & 2D Stokes sphere & \ref{sec:sphere} \\
    Sticky air and  & Stabilisation algorithm & \ref{sec:stab} \\
    free surface & Topography relaxation & \ref{sec:crameri} \\
  & Spontaneous subduction & \ref{sec:subduction} \\
\hline
  Erosion and sedimentation  & - & - \\
\hline
   Non-linear  & Slab detachment & \ref{sec:slab} \\
   visco-plasticity & Indenter & \ref{sec:indenter} \\
    & Brick & \ref{sec:brick} \\
\hline
  \multirow{3}{*}{Energy equation}  & Advection stabilisation & \ref{sec:advection} \\
    & Simple shear heating & \ref{sec:simple_shear} \\
    & Shear and adiabatic heating & \ref{sec:shear} \\
\hline
\multirow{3}{*}{Energy + momentum} & Mantle convection & \ref{sec:mantle} \\
& Thin layer entrainment & \ref{sec:thin} \\
& Viscoplastic mantle convection & \ref{sec:visco_mantle} \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder} & \multirow{2}{*}{\ref{sec:quinquis}} \\
  and hydration  &  & \\
\hline
  Melting & Experimental melting curves & \ref{sec:katz} \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}

@@

\subsection{Mantle convection}\label{sec:mantle}
This problem is performed as presented by \citet{Blankenbach1989} (constant viscosity cases) and \citet{Thieulot2014}, in a 2D unit square domain with gravity
acceleration $g_y=10^{10}Ra$. The experiment is performed with three different Rayleigh numbers ($Ra=10^4$, $10^5$ and $10^6$) and with different grid
resolution (between \num{32x32} and \num{128x128} elements). Both fluids have constant viscosity, initial density, heat capacity, thermal conductivity
($\eta= \rho_0= C_p = k=1$), reference temperature ($T_0=0$) and thermal expansion coefficient ($\alpha=10^{-10}$). Temperatures are set to 0 on top and 1 on
bottom of the domain. Velocity boundary conditions are set to free slip on all sides. The initial temperature field is given by
\[T(x,y)=(1-y)+0.01 \cos (\pi x) \sin (\pi y)\]

@@

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as Cases 1-5a described in \citet{Tosi2015}. Table \ref{tab:tosi_setup}. Table \ref{tab:visco_mantle}.WORK IN PROGRESS.

@@

  \caption{Results of the viscoplastic mantle convection benchmark for different grid resolutions in Cases 1-4 compared with results obtained with ELEFANT

@@

@@

\subsection{Melting curves}\label{sec:katz}
This instantaneous experiment is performed in order to recreate isobaric melting curves, as function of temperature, bulk water and content of water in the
melt, to compare with melting curves obtained by \citet{Katz2003}. The domain is square with $L_x=L_y=100$ km, a grid resolution of \num{100x100} elements and
25 markers per element. Density is set in the entire domain to \SI{3300}{\kg\per\cubic\m} and temperature increases from the sides to the centre from 1000° to
1500°C. The experiment is performed for bulk water contents from 0 to 0.3 wt.\%.

Fig. \ref{fig:fraction} shows isobaric melting curves for \SI{1}{\giga\pascal} (panel a) and \SI{3}{\giga\pascal} (panel b) calculated for different bulk water
contents. The curves well match with those obtained by \citet{Katz2003}, showing the saturation at the solidus for bulk water of 0.2 and 0.3 wt.\%, indicating
that the code correctly determines melt fraction as function of pressure, temperature and bulk water content. Same results can be observed in Fig.
\ref{fig:water}a, where isobaric and isothermal melting curves are shown as function of bulk water content. In addition, Fig. \ref{fig:water}b shows that the
code correctly determines also the percentage of water in the melt as function of pressure, temperature and melt fraction.

>>>>

\begin{table}[H]
\caption{List of benchmarks implemented for each feature of the code.}
\centering
\begin{tabular}{| l | l | l |}
\toprule
 \textbf{Feature}  & \textbf{Benchmark} & \textbf{Section} \\
\midrule
  Solver  & Stokes flow & \ref{sec:stokes} \\
\hline
  4th-order Runge-Kutta  & \multirow{2}{*}{Zalesak disk} & \multirow{2}{*}{\ref{sec:runge}} \\
  markers advection  &  & \\
\hline
  \multirow{4}{*}{Momentum equation}  & Poiseuille flow & \ref{sec:poiseuille}\\
    & Instantaneous 2D sphere & \ref{sec:ist_sphere} \\
    & Rayleigh-Taylor experiment & \ref{sec:rayleigh} \\
    & Falling block & \ref{sec:block} \\
\hline
    & 2D Stokes sphere & \ref{sec:sphere} \\
    Sticky air and  & Stabilisation algorithm & \ref{sec:stab} \\
    free surface & Topography relaxation & \ref{sec:crameri} \\
  & Spontaneous subduction & \ref{sec:subduction} \\
\hline
  Erosion and sedimentation  & - & - \\
\hline
   Non-linear  & Slab detachment & \ref{sec:slab} \\
   visco-plasticity & Indenter & \ref{sec:indenter} \\
    & Brick & \ref{sec:brick} \\
\hline
  \multirow{3}{*}{Energy equation}  & Advection stabilisation & \ref{sec:advection} \\
    & Simple shear heating & \ref{sec:simple_shear} \\
    & Shear and adiabatic heating & \ref{sec:shear} \\
\hline
\multirow{3}{*}{Energy + momentum} & Mantle convection & \ref{sec:mantle} \\
& Viscoplastic mantle convection & \ref{sec:visco_mantle} \\
& Thin layer entrainment & \ref{sec:thin} \\
\hline
  Phase changes  & \multirow{2}{*}{Hydrated sinking cylinder} & \multirow{2}{*}{\ref{sec:quinquis}} \\
  and hydration  &  & \\
\hline
  Melting & Experimental melting curves & \ref{sec:katz} \\
\bottomrule
\end{tabular}
\label{tab:list}
\end{table}

@@

\subsection{Mantle convection}\label{sec:mantle}
This problem is performed as presented by \citet{Blankenbach1989} (constant viscosity cases) and \citet{Thieulot2014}, in a 2D unit square domain with gravity
acceleration $g_y=10^{10}Ra$. The experiment is performed with three different Rayleigh numbers ($Ra=10^4$, $10^5$ and $10^6$) and with different grid
resolution (between \num{32x32} and \num{128x128} elements). The fluid has constant viscosity, initial density, heat capacity, thermal conductivity
($\eta= \rho_0= C_p = k=1$), reference temperature ($T_0=0$) and thermal expansion coefficient ($\alpha=10^{-10}$). Temperatures are set to 0 on top and 1 on
bottom of the domain. Velocity boundary conditions are set to free slip on all sides. The initial temperature field is given by
\[T(x,y)=(1-y)+0.01 \cos (\pi x) \sin (\pi y)\]

@@

\subsection{Viscoplastic mantle convection}\label{sec:visco_mantle}
This benchmark is performed as Cases 1-5a described in \citet{Tosi2015} in a 2D unit square domain with two different grid resolutions of \num{32x32} 
and \num{100x100} elements. Reference viscosity, reference density, heat capacity, thermal conductivity and thermal expansion coefficient are fixed to a constant
value of 1 ($\eta_0= \rho_0= C_p = k=\alpha=1$), while the gravity has been chosen as $g_y=10^2$, in order to obtain a Rayleigh number $Ra=10^2$. Temperatures
are set to 0 on top and 1 on bottom of the domain. Velocity boundary conditions are set to free slip on all sides. The initial temperature field is given by
\[T(x,y)=(1-y)+0.01 \cos (\pi x) \sin (\pi y)\].
The viscosity ﬁeld $\eta$ is calculated as the harmonic average between a linear part $\eta_{lin}$ that depends on temperature only or on temperature and 
depth $y$ and a nonlinear-plastic part $\eta_{pl}$ that depends on the strain rate $\dot{\bm{\epsilon}}$, as follows
\[\eta(T,y,\dot{\bm{\epsilon}})=2\left(\frac{1}{\eta_{lin}(T,y)}+\frac{1}{\eta_{pl}(\dot{\bm{\epsilon}})}\right)^{-1}\]
The linear and the nonlinear-plastic parts of the viscosity are calculated following \citet{Tosi2015} as follows
\[\eta_{lin}(T,y)=\exp(-\ln(\Delta\eta_T)T+\ln(\Delta\eta_y)y)\]
\[\eta_{pl}(\dot{\bm{\epsilon}})=\eta^*+\frac{\sigma_Y}{\sqrt{\dot{\bm{\epsilon}}:\dot{\bm{\epsilon}}}}\]
where $\Delta\eta_T$, $\Delta\eta_y$, $\eta^*$ and $\sigma_Y$ are parameters chosen as listed in Table \ref{tab:tosi_setup}.

For each case, some diagnostic quantities measured at the steady state are reported in Table \ref{tab:visco_mantle} (see Section \ref{sec:error} for 
the computation of all the quantities), showing a well fit with results described in \citet{Tosi2015}.

@@

  \caption{Results of the viscoplastic mantle convection benchmark for different grid resolutions in Cases 1-5 compared with results obtained with ELEFANT

@@

       \multicolumn{13}{|c|}{\textbf{Case 5}} \\
       Code & Resolution & $P$ & $\left\langle T \right\rangle_{min}$ & $\left\langle T \right\rangle_{max}$ & Nu$^{top}_{min}$ & Nu$^{top}_{max}$ &
       $v_{\textrm{rms}}^{min}$ & $v_{\textrm{rms}}^{max}$ & \multicolumn{2}{c}{$(\left\langle \Phi \right\rangle/Ra)_{min}$} & 
       \multicolumn{2}{c|}{$(\left\langle \Phi \right\rangle/Ra)_{max}$} \\
         YACC & $100\times100$ & 0.0792 & 0.6543 & 0.6722 & 2.6950 & 7.2792 & 41.9813 & 98.8230 & \multicolumn{2}{c}{1.4347} & 
         \multicolumn{2}{c|}{9.2748} \\
         ELEFANT & $100\times100$ & 0.076 & 0.6514 & 0.6693 & 2.6808 & 7.3506 & 41.2578 & 100.089 & \multicolumn{2}{c}{1.3324} & 
         \multicolumn{2}{c|}{9.5289} \\
         Stone 28 & $32\times32$ & 0.0764 & 0.6521 & 0.6697 & 2.6912 & 7.0763 & 41.61 & 98.183 & \multicolumn{2}{c}{-} & 
         \multicolumn{2}{c|}{-} \\
     %    FALCON & $32\times32$ & & 0.7750 & 3.4381 & 2.7363 & 248.3337 & 2.0022 & 2.7813 & \multicolumn{2}{c}{-} & 
     %     \multicolumn{2}{c|}{-} \\
         FALCON & $100\times100$ & 0.0775 & 0.6519 & 0.6697 & 2.6847 & 7.3629 & 41.5256 & 99.5466 & \multicolumn{2}{c}{1.3399} & 
         \multicolumn{2}{c|}{9.3993} \\

@@

\subsection{Mantle melting curves}\label{sec:katz}
This instantaneous experiment is performed in order to recreate isobaric melting curves, as function of temperature, bulk water and content of water in the
melt, to compare with melting curves obtained by \citet{Katz2003}. The domain is square with $L_x=L_y=100$ km, a grid resolution of \num{100x100} elements and
25 markers per element. Density is set in the entire domain to \SI{3300}{\kg\per\cubic\m} and temperature increases from the sides to the centre from 1000° to
1500°C. The experiment is performed for bulk water contents from 0 to 0.3 wt.\%.

Fig. \ref{fig:fraction} shows isobaric melting curves for \SI{1}{\giga\pascal} (panel a) and \SI{3}{\giga\pascal} (panel b) calculated for different bulk water
contents. The curves well match with those obtained for the mantle by \citet{Katz2003}, showing the saturation at the solidus for bulk water of 0.2 and 0.3 wt.\%, indicating
that the code correctly determines melt fraction as function of pressure, temperature and bulk water content. Same results can be observed in Fig.
\ref{fig:water}a, where isobaric and isothermal melting curves are shown as function of bulk water content. In addition, Fig. \ref{fig:water}b shows that the
code correctly determines also the percentage of water in the melt as function of pressure, temperature and melt fraction.
